% !TEX root = mythesis.tex

%==============================================================================
\chapter{Faint laser source for detector characterization}
\label{sec:SNSPD_setup}
%==============================================================================

Counting photons one has to consider the characteristics of the emitter source as well.
Here I focus only on the characteristics of a laser source affecting the characterization I made.
For this first, I briefly sum up characteristics of a laser light source and its conditions it gives us for our detector
characterization.
Further, I make considerations regarding the inherent blindspots of laser light due to the randomness nature of photons
in coherent light.
Afterward, I introduce the setup I build for characterizing our SNSPD.\\

\section{Characteristics of faint laser sources}

Using a laser source enables us, considering the emitting light as monochromatic beam with angular frequency $\omega$
and constant Intensity I. The Photon flux of a laser is defined as the photon average number passing through
a cross-section in unit time:

\begin{align}
    \Phi = \frac{I A}{\hbar \omega} = \frac{P}{\hbar \omega} \text{photons $s^{-1}$}
\end{align}

where \textit{I} is the current of photon, \textit{A} the cross-section, \textit{P} the laser power and $\omega$ the angular frequency which
depends on the wavelength.

The average number of registered counts $N(T)$ for a given detection time T by a detector is given by:

\begin{align}
    \text{N(T)} = \text{T} \Phi \eta= \frac{P T \eta}{\hbar \omega} \text{photons}
\end{align}

and hence the registered counts $\mathbb{R}$ per unit time by:

\begin{align}
    \mathcal{R} = \frac{\text{N(T)}}{\text{T}} = \eta \Phi= \frac{P \eta}{\hbar \omega} \text{photons  $s^{-1}$}
\end{align}

where \textit{$\eta$} is the efficiency of the detector system.

This detection count rate is restricted by the largest amount on the dead time of the detector.

\begin{align}
    \mathcal{R_{\max}} \propto \frac{1}{\tau_{d}}
\end{align} \\

Because the used laser has a minimum threshold power which corresponds to a photonrate above the maximum one,
one has to attenuate the laser power in order to detect all events.

The photon statistic of coherent light, in our case (in reasonable approximation) of our laser light,
is given by poisson statistics.
This characteristic stems from discrete nature of photons and hence non-equidistant spacing between photons.
Measuring single photons, one has to ensure that we have a neglectable amount of photons in the segment
of the deadtime because else our light characteristics inherently forbid us measuring each of the incoming photons.\\

This is calculated by looking at the propability of measuring one photon per length segment, given by the deadtime.
First, we consider one Length segment given by the deadtime $\tau_{\text{d}}$ and the measurement time $\tau_{\text{m}}$:
\begin{align}
    L_{\text{d}} = \frac{c}{\tau_{\text{d}}}\\
    L_{\text{m}} = \frac{c}{\tau_{\text{m}}}
\end{align}

Through this, we can calculate for a given measurement time the average photon rate per length segment $L_{\text{m}}$
and further the probability of finding one photon in the particular line segment $L_{\text{d}}$:

\begin{align}
    \bar{n} = \Phi \frac{L_{\text{m}}}{c}\\
    p = \frac{\bar{n}}{\text{N}}
\end{align}

Where $N = \frac{c}{L_{\text{d}}}$ are the subsegments of the measured length segment $L_{\text{m}}$.

This enables us to calculate the probability p of finding n Photons per deadtime segment $L_{\text{d}}$ and
including this in our measurements.

\section{Experimental setup}

Though not measured by ourselves first, it is known from \textcolor{red}{Zitat} deadtime of the detector is around 20-25ns.
This gives us a theoretical maximum detection rate of $\mathcal{R_{\max}} \propto \frac{1}{\tau_{d}} = 25-50\si{M\Hz}$.
In order to realize the laser attenuation the following setup was build:

The first coupling of the laser light was done in order to operate with the beam on a lower stage, because the laserbeam 
was due to its construction on an uplifted stage. 
Afterward the beam passes a pbs to filter the horizontal polarized E field out. 
Further a galile telescope was build out of one focal and one diffusing lens for minimizing the beam width so it fits fully 
on the surface of the AOM crystal. The first order of the AOM was set for flexible voltage modulation of the laser.
A cover was used to filter out the first from the zeroth order of the AOM. Then a flip mount was placed, where 
Neutral density (ND) filers could be placed in and flexible placed in and out of the laser beam. 
The ND filters have the function to attenuate the laser light. 
At the end, before the laser light was again coupled in two waveplates where used to stabilize the light polarization regarding the
slow axis of the fibre. Afterwards the light was coupled back into a fibre, so it can be send to the detector.
It was important that the light was coupled in to a APC/PC to FC/PC optical fibre because the detector only had a FC/PC optical fibre
input, in order to maintain higher efficiency coupling in the light.\\

Besides, this optical setup had to be protected from environmental light. For this, the room where the setup was running was shielded 
with alu foil which has a reflection coefficient of almost 90$\%$ at the operating wavelenght of 780nm. 
Morverover a black box was build. It has the function to avoid further environmental light coupling into the fibre. Additionally, 
the optical fibre running from the optical setup to the detector was shielded with alu foil as well to avoid absoption from the optical 
fibre. 



%Relying on: https://nano-optics.physik.uni-siegen.de/education/teaching/lab_courses/sps-exp-manual.pdf

- Basics of photon distribution of laser, attenuation, poisson statistics \\
- Set up for laser attenuation \\
- Single Photon Detection paper \\



